Excuse me, do you have a moment to talk about version control?

### 2017-05-29 README.Rmd
Cite Ten Simple Rules for Taking Advantage of Git and GitHub

Git has been re-purposed by the data science community [@Ram2013;
@git-for-humans]. In addition to using it for source code, we use it to manage 
the motley collection of files that make up typical data analytical projects, 
which often consist of data, figures, reports, and, yes, source code. Even those
who identify more as statistician than data scientist generally have a similar 
mix of files that are the artifacts of a project.

@@

>>>>

Git has been re-purposed by the data science community [@Ram2013;
@git-for-humans; @ten-simple-rules-git]. We use it to manage the motley collection of files that make up typical data analytical projects, which often consist of data, figures, reports, and, yes, source code. Even those who identify more as statistician than data scientist generally have a similar mix of files that are the artifacts of a project.

@@

A Quick Introduction to Version Control with Git and GitHub
http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004668
